-
title: "Larval Krill Chamber Exposure Pilot Project Fresh Water SPEC plots"
output:
 html_document:
    df_print: paged
    code_folding: hide
    toc: TRUE
    toc_depth: 4
    toc_float: true
    theme: cerulean
    highlight: haddock
    smart: false
editor_options: 
  chunk_output_type: inline
---


Hello World

Author: OA Lab, NWFSC
Title: Larval Krill Chamber Exposure Pilot Project Fresh Water SPEC plots


# Version Check
```{r 0.1 Version Check , echo=FALSE, results=FALSE, message=FALSE, warning=FALSE}
#*********************************
## Version Check
#********************************* 
R.version

```




# Libraries
```{r 0.0 Libraries , echo=FALSE, results=FALSE, message=FALSE, warning=FALSE}
#*********************************
##Libraries
#********************************* 
library(stringr)
library(tidyverse)
library(plyr)
library(nlme)
library(tidyr)
library(dbplyr)
library(dplyr)
library(purrr)
library(wql)
library(lubridate)
library(tibbletime)
library(arsenal)
library(compareDF)
library(todor)
library(data.table)
#for graphing
library(ggplot2)
library(ggfortify)
library(stringr)
library(nlme)
library(RColorBrewer)
library(patchwork)
#statistical analysis
library(gdata)
library(rsq)
library(doBy)
library(lme4)
library(lmerTest)
#Rnotebooks 
library(gridExtra)
library(kableExtra)
library(todor)
#metadata
library(metacsv)

```



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



# 1.) Setting Working Directory
```{r 1.) Setting Working Directory, echo=FALSE, results=FALSE, message=FALSE, warning=FALSE }
#*********************************
## 1.) Setting Working Directory
#*********************************

#set working directory to the correct folder
setwd("/Users/katherinerovinski/Documents/GitHub/Krill-pilot-2021/data")
getwd()


```



# 2.) Dataframe 
```{r 2.) Creating the initial Dataframe}
#*********************************
## 2.) Creating the initial Dataframe
#*********************************
#set working directory to the correct folder

setwd("/Users/katherinerovinski/Documents/GitHub/Krill-pilot-2021/data")
freshSPEC <- read_csv(here::here("data", "SPECsimpleJarTestResults.csv"))
write_meta_template(freshSPEC, here::here("data","SPECsimpleJarTestResults"))

#|- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - |

```


```{r}

p <- ggplot(freshSPEC, aes(ID_1, pH))  + 
            geom_jitter(data = freshSPEC, aes(ID_1, pH)) +
            xlab("Bottle or Jar(well)") +
            ylab("pH (not corrected)") +
            ggtitle("Simple Fresh Carbonated Water Test") +
            theme_bw() 

p


p3 <- ggplot(freshSPEC, aes(ID_1, pH)) +
            geom_jitter(color = "grey") +
            geom_boxplot(notch = TRUE, outlier.shape = NA, colour = "blue") +
            # facet_wrap(~TrialID) +
            ggtitle("Simple Fresh Carbonated Water Test") +
            theme_bw()


p3


```




```{r}

p4 <- ggplot(freshSPEC, aes(ID_2, pH))  + 
            geom_jitter(data = freshSPEC, aes(ID_2, pH)) +
            # xlab("Bottle or Jar(well)") +
            # ylab("pH (not corrected)") +
            ggtitle("Simple Fresh Carbonated Water Test") +
            theme_bw() 

p4


```




```{r}

p5 <- ggplot(freshSPEC, aes(ID_3, pH))  + 
            geom_jitter(data = freshSPEC, aes(ID_3, pH)) +
            # xlab("Bottle or Jar(well)") +
            # ylab("pH (not corrected)") +
            ggtitle("Simple Fresh Carbonated Water Test") +
            theme_bw() 

p5


```









```{r}
#**************E*N*D*************# 
#*********************************
## END OF SCRIPT | END OF DOCUMENT 
#*********************************
```


## END OF SCRIPT | END OF DOCUMENT

