-
title: "Larval Krill Chamber Exposure Pilot Project CTD Data 2021 graphs"
output:
 html_document:
    df_print: paged
    code_folding: hide
    toc: TRUE
    toc_depth: 4
    toc_float: true
    theme: cerulean
    highlight: haddock
    smart: false
editor_options: 
  chunk_output_type: inline
---


Hello World

Author: OA Lab, NWFSC
Title: Larval Krill Chamber Exposure Pilot Project CTD Data 2021 graphs


# Version Check
```{r 0.1 Version Check , echo=FALSE, results=FALSE, message=FALSE, warning=FALSE}
#*********************************
## Version Check
#********************************* 
R.version

```




# Libraries
```{r 0.0 Libraries , echo=FALSE, results=FALSE, message=FALSE, warning=FALSE}
#*********************************
##Libraries
#********************************* 
library(stringr)
library(tidyverse)
library(plyr)
library(nlme)
library(tidyr)
library(dbplyr)
library(dplyr)
library(purrr)
library(lubridate)
library(tibbletime)
library(data.table)
#for graphing
library(ggplot2)
library(stringr)
library(nlme)
library(patchwork)
#Rnotebooks 
library(gridExtra)
library(kableExtra)

```



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



# 2.) Dataframe 
```{r 2.) Creating the initial Dataframe}
#*********************************
## 2.) Creating the initial Dataframe
#*********************************
#set working directory to the correct folder

CTD_log_0623 <- read_csv(here::here("data", "CTD_data_0623.csv"))
write_meta_template(CTD_log_0623, here::here("data","CTD_data_0623"))

#|- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - |

```





# 3.) By Depth Plots 
```{r 3.) CTD plots by depth}
#*********************************
## 3.) CTD plots by depth 
#*********************************

names(CTD_log_0623)
# [1] "Pressure_(Decibar)"                                 "Depth_(Meter)"                                     
# [3] "Temperature_(Celsius)"                              "Conductivity_(MicroSiemens.per.Centimeter)"        
# [5] "Specific_conductance_(MicroSiemens.per.Centimeter)" "Salinity_(Practical.Salinity.Scale)"               
# [7] "Sound_velocity_(Meters.per.Second)"                 "Density_(Kilograms.per.Cubic.Meter)"


# CTD_log_0623 %>%
#   rename(
#     Depth_(Meter) = depth,
#     Temperature_(Celsius) = temperature,
#     Salinity_(Practical.Salinity.Scale) = salinity
#     )


# names(CTD_log_0623)[names(CTD_log_0623) == "Depth_(Meter)"] <- "depth"
# names(CTD_log_0623)[names(CTD_log_0623) == "Temperature_(Celsius)"] <- "temperature"
# names(CTD_log_0623)[names(CTD_log_0623) == "Salinity_(Practical.Salinity.Scale)"] <- "salinity"
# 
# 
# rename(CTD_log_0623, temperature = Temperature_(Celsius))
# rename_with(CTD_log_0623, "temperature", starts_with("Temperature_"))
# 
# rename(CTD_log_0623, temperature = Temperature_(Celsius))

CTD_log_0623_clean <- CTD_log_0623 %>%
  dplyr::rename(new_temperature = temperature)

p <- ggplot(CTD_log_0623, aes(temperature, depth))  + 
            geom_jitter(data = CTD_log_0623, aes(temperature, depth)) +
            xlab("Temperature (Celsius)") +
            ylab("Depth (meters)") +
            ggtitle("(6/23/21) CTD Thermocline") +
            theme_bw() 

p
#|- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - |


```



```{r}

p1 <- p + scale_y_reverse()


```





```{r}
q1 <- ggplot(CTD_log_0623, aes(salinity, depth))  + 
            geom_jitter(data = CTD_log_0623, aes(salinity, depth)) +
            xlab("Salinity (Practical Salinity Scale)") +
            ylab("Depth (meters)") +
            ggtitle("(06/23/21) CTD Salinity Plot") +
            scale_y_reverse() +
            theme_bw() 

q1
```

```{r}
p1 + q1
```






```{r}
#**************E*N*D*************# 
#*********************************
## END OF SCRIPT | END OF DOCUMENT 
#*********************************
```


## END OF SCRIPT | END OF DOCUMENT
















